\cvsection{Work Experience}

\begin{cventries}

  \cventry
  {Lead Software Engineer} % Job title
  {\href{https://terazo.com}{Terazo}} % Organization
  {Richmond, VA} % Location
  {Jul 2017 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and lead the implementation of a microservice architecture
      based on the principles of REST and Contact-First Development.}
      \item {Mentored a large team of software engineers and championed best
      practices including TDD and SOLID Design.}
      \item {Achieved high quality and rapid iteration by using a Test
      Driven approach and maintaining a comprehensive suite of automated tests.}
      \item {Developed Event-Driven Architecture utilizing Kafka to broadcast
      entity changes and Kafka Streams library to build robust stream
      processors.}
      \item {Designed workflow automation system allowing for the construction
      of highly dynamic and scenario driven consumer outreach process.}
    \end{cvitems}
  }

  \cventry
  {Senior Software Engineer} % Job title
  {\href{https://www.forrent.com}{ForRent.com}} % Organization
  {Norfolk, VA} % Location
  {Feb 2012 - Jul 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Guided the development of APIs throughout the company. Directed a
      team of engineers working on key infrastructure.}
      \item {Presented training on technical topics and introduced new standards
      an practices.}
      \item {Established reusable pattern for development of RESTful
      microservices using Spring Boot and guided the replacement of legacy
      applications.}
      \item {Led replacement of vendor search engine with a faster, more
      flexible API built with Spring Boot and Elasticsearch.}
      \item {Designed and implemented API to facilitate Community Messenger
      product. API was flexible and scalable enough to allow for rapid user
      growth and feature addition with minimal additional work.}
      \item {Collaborated with teams throughout company on migration to a stream
      based architecture using Apache Kafka. Replaced legacy ETL processes with
      publishers and subscribers using Logstash.}
      \item {Designed schema and integrated applications with multiple different
      database technologies, including Elasticsearch, SQL Server, MongoDB, and
      Redis.}
      \item {Used test driven approach to build reliable software using the
      testing tools PHPUnit, NUnit, JUnit, Mocha, Mockito, and Sinon.JS}
    \end{cvitems}
  }

  \cventry
    {Programmer/Developer I} % Job title
    {\href{https://www.dominionenterprises.com}{Dominion Enterprises}} % Organization
    {Norfolk, VA} % Location
    {May 2009 - Feb 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built corporate training website using Drupal CMS.
        Supported content administration and developed custom Drupal plugins.}
        \item {Maintained and supported numerous internal systems including
        Human Resources website.}
        \item {Implemented OpenID and LDAP authentication system to provide SSO
        access to internal resources.}
        \item {Integrated applications with vendor web services.}
        \item {Performed database (MS SQL Server) and server (IIS)
        administration tasks.}
        \item {Developed job posting portal, allowing hiring managers to
        advertise jobs and collect applications.}
      \end{cvitems}
    }

\end{cventries}
